How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-08-31 paper.tex
fixed typo

This paper has focused on what software consumers should do when asking for
help.  I suppose it could even be read as a list of complaints about bad
behavior by users (though that's not how I intend it). However, each behavior
described above has a corresponding expectation for the developers. If we expect
the users to try to solve their own problem, it behooves us to write good
document, give examples, and (most importantly) keep them up to date. If we want
to be contacted via GitHub only, we need to make that information clear and easy
to find. If we are frustrated by bug reports that don't give us the information
we need, we should tell people what kinds of information we need (e.g. by
providing bug report templates). In order to receive proper credit, we need to
document the appropriate way to cite the software. All of this information needs
to be clearly written out and easy to find.

>>>>

This paper has focused on what software consumers should do when asking for
help.  I suppose it could even be read as a list of complaints about bad
behavior by users (though that's not how I intend it). However, each behavior
described above has a corresponding expectation for the developers. If we expect
the users to try to solve their own problem, it behooves us to write good
documentation, give examples, and (most importantly) keep them up to date. If we
want to be contacted via GitHub only, we need to make that information clear and
easy to find. If we are frustrated by bug reports that don't give us the
information we need, we should tell people what kinds of information we need
(e.g. by providing bug report templates). In order to receive proper credit, we
need to document the appropriate way to cite the software. All of this
information needs to be clearly written out and easy to find.
